\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-05 doc/paper.tex
remove comment about mu, Bmu in the initial guess
correcting descr. of initial guess for Yukawa couplinges

  $y_{u,d,e}$ of the SUSY model are set to the known Standard Model
  Yukawa couplings (ignoring SUSY radiative corrections).

@@

  is set to zero. {\color{red} Is $B\mu$ set to zero, this would be weird and from looking I think it is $A_0$.}
  \JHrem{The C++ code does set $B\mu$ to zero.  Moreover, it sets $\mu$ to +1 GeV irrespective of SignMu.  This should be no problem as long as the solution is found though.}

>>>>

  $y_{u,d,e}$ of the SUSY model are set from the known Standard Model
  Yukawa couplings using the tree-level relations (ignoring SUSY
  radiative corrections).

@@

  is set to zero.
